Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training

### 2024-12-06 manuscript/manuscript.Rmd
plot settings update

```{r plot-settings}
## theme settings for ggplot
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18), 
          title = element_text(size = 18),
          legend.position = "bottom")
)

>>>>

```{r plot-settings}
## theme settings for ggplot
theme_set(
  theme_bw() +
    theme(text = element_text(size = 18, face = "bold"), 
          title = element_text(size = 18, face = "bold"),
          legend.position = "bottom")
)
